\documentclass[11pt,letterpaper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{burgundy}

\firstname{Matthieu}
\lastname{Grieger}
\title{Software Development Engineer}
\email{me@matthieugrieger.com}
\homepage{matthieugrieger.com}
\social[github]{matthieugrieger}
\social[linkedin]{matthieugrieger}

\usepackage[scale=0.75]{geometry}

\begin{document}
	\makecvtitle
	
	\section{Education}
	\cventry{2012--2016}{B.S. Computer Science}{Seattle Pacific University}{Seattle, WA}{}{-- Computer Engineering Minor\\-- 3.93 GPA, Summa Cum Laude\\-- Member of Alpha Kappa Sigma honor society\\-- Recipient of Ken Smith Sr. Scholarship\\-- Dean's List every quarter}
	
	\section{Experience}
	\cventry{2016--present}{Software Development Engineer}{Amazon}{Seattle, WA}{}{}
	\cventry{2013--2016}{Tech Desk Consultant}{Seattle Pacific University Library}{Seattle, WA}{}{-- Helped students and faculty with technology related questions.\newline{-- Helped maintain metadata for an archive of over 3,000 audio/video files.}}
	\cventry{Summer 2015}{Software Development Engineer Intern}{Amazon}{Seattle, WA}{}{-- Member of Transactional Foreign Exchange (TFX) team within Amazon Payment Products.\newline{-- Created a caching library that cached exchange rates to improve latency of TFX API calls.}\newline{-- Technologies used: Java, Spring Framework, Junit, Mockito, Hibernate, Git}}
	
	\section{Skills}
	\cvitem{\textbf{Languages}}{Go, Python, Java, C/C++, HTML/CSS, Javascript, \LaTeX}
	\cvitem{\textbf{Systems}}{Linux (Arch, Debian, RHEL), Windows XP/7/8/10, Mac OS X}
	\cvitem{\textbf{Applications}}{Git, IntelliJ IDEA, Visual Studio, Atom, \LaTeX, PostgreSQL, MySQL, Redis, Flask}
	\cvitem{\textbf{Misc.}}{Strong written and verbal communication skills, excellent troubleshooting and debugging skills, great problem solving skills}
	
	\section{Projects}
	\cvitem{Go}{\textbf{MumbleDJ} -- github.com/matthieugrieger/mumbledj\newline{A Mumble bot that plays music fetched from various audio \& video sites.}}
	\cvitem{Python, JS}{\textbf{VideoLocale} -- github.com/Team-95/videolocale\newline{A website that allows users to search for YouTube videos by selecting geographical regions on a map.}}
\end{document}